---
title: "Advanced Filters"
author: "Johann de Boer"
date: "2018-09-09"
output:
  html_vignette:
    keep_md: true
  md_document:
    variant: markdown_github
vignette: >
  %\VignetteIndexEntry{ADVANCED FILTERS}
  %\VignetteEngine{knitr::knitr_notangle}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
# source: https://stackoverflow.com/a/46482580/1007029
is_check <- ("CheckExEnv" %in% search()) || any(c("_R_CHECK_TIMINGS_",
             "_R_CHECK_LICENSE_", "TRAVIS") %in% names(Sys.getenv()))
knitr::opts_chunk$set(eval = !is_check, purl = !is_check)
```

`ganalytics` provides functions that makes it easy to define filters using natural R language operators. This example shows how to use `ganalytics` to define dimension or metric filters that can be used by the `googleAnalyticsR` package. The current development version of `googleAnalyticsR` supports filters defined with `ganalytics`.

## Setup/Config

Once installed, load these packages. Please refer to the `googleAnalyticsR` package documentation on configuration steps you may need to complete in order to use the Google Analytics APIs.

```{r setup}
library(googleAnalyticsR)
library(ganalytics)
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)
library(knitr)

ga_auth(file.path("~", "ga.oauth"))

view_id <- "117987738"
start_date <- "2018-05-01"
end_date <- "2018-06-30"
```

