---
title: "Management API"
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# auto-auth when done locally
library(googleAnalyticsR)
```

The Management API v3 covers all API calls that are not data reporting related and are for getting meta information about your Google Analytics account or to change account settings.

## Account structure

Shows the details for your account structure (`Accounts > Web-properties > Views (profiles)`) including creation time, user permissions etc.

The most day-today useful function below is `ga_account_list()` which summarises all account web properties and views avaialble to your user. 

* `ga_account_list()`	- Get account summary including the ViewId
* `ga_accounts()`	- Get account metadata for your user
* `ga_webproperty()` -	Get web property 
* `ga_webproperty_list()` -	List web properties for a particular accountId
* `ga_view()` - Get single View (Profile)
* `ga_view_list()` -	List Views (Profile) for a particular accountId/webPropertyId

You can then also get the meta-data for that particular entity via `ga_webproperty()` or `ga_view()`

```{r account structure, message=FALSE, warning=FALSE}
# you will usually want this one that summarises all accounts, webproperties and views available to your user
# (restricted to top 10 with the head() function)
head(ga_account_list(), n = 10)

# this only lists account meta-data
ga_accounts()

# this gives meta-data for all web-properties for this accountId
ga_webproperty_list(47480439)

# this is meta-data for one particular web-property
ga_webproperty(accountId = 47480439, webPropertyId = "UA-47480439-1")

# this is meta-data for the views under this accountId/webPropertyId
ga_view_list(accountId = 47480439, webPropertyId = "UA-47480439-1")

# this is meta-data for this particular viewId (profileId)
ga_view(accountId = 47480439, webPropertyId = "UA-47480439-1", profileId = 81416941)
```


## Helper functions

These are helper utility functions to work with Google Analytics reporting API data.

* `google_analytics_meta()` - get a data.frame of available dimensions and metrics, or just use `meta` directly to get the version that comes with the library.


```{r}
# you can just use `meta` as is to get the available metrics, or ensure an up to date version by calling the metadata API.
# here we just return the first 5 columsn and rows for brevity
head(meta[,1:5])

head(google_analytics_meta())[,1:5]
```

* `aggregateGAData()` - aggregate data down to the dimensions you specify, treating metrics correctly regarding if they should be averaged or summed. This is used internally when using anti-sampling, and is also useful to respond to dimension selections in Shiny dashboards, where you don't want to perform a new API call each time you need aggregated data.  Download all data first in a more unaggregated form, then use this function.

```{r}
# use `aggregateGAData` so you can on the fly create summary data
ga_data <- google_analytics(81416156, 
                            date_range = c("10daysAgo", "yesterday"),
                            metrics = c("sessions","bounceRate"), dimensions = c("hour","date"))

head(ga_data)

# if we want totals per hour over the dates:
aggregateGAData(ga_data[,c("hour","sessions")], agg_names = "hour")

# it knows not to sum metrics that are rates:
aggregateGAData(ga_data[,c("hour","bounceRate")], agg_names = "hour")
```


* `allowed_metric_dim()` - Create named list of allowed GA metrics/dimensions.  This is useful to have nice looking labels for dimension and metric selection pickers, or to create lookup tables.

```{r}
#
amd <- allowed_metric_dim()
head(amd)
```

## AdWords

* `ga_adwords()`	Get AdWords Link meta data
* `ga_adwords_list()`	List AdWords

## Custom Data Sources

See and upload custom data sources to Google Analytics

* `ga_custom_datasource()`	- List Custom Data Sources
* `ga_custom_upload()`	- Custom Data Source Upload Status
* `ga_custom_upload_file()`- Upload a file to GA custom uploads
* `ga_custom_upload_list()` - List the files in a GA custom upload

## Custom variables

Custom variables for a Google Analytics property.

* `ga_custom_vars()` - get meta data for a specific custom variable
* `ga_custom_vars_list()` - list all custom variables.


## Experiments

* `ga_experiment()`	- Experiments Meta data
* `ga_experiment_list()`	- List Experiments

## View Filters

The filter edit functions are contributed by @zselinger which allow you to update filters for your Google Analytics views at scale. 

* `ga_filter()`	- Get specific filter for account
* `ga_filter_add()`	- Create a new filter and add it to the view (optional).
* `ga_filter_apply_to_view()`	- Apply an existing filter to view.
* `ga_filter_delete()`	- Delete a filter from account or remove from view.
* `ga_filter_list()`	- List filters for account
* `ga_filter_update()`	- Updates an existing filter.
* `ga_filter_update_filter_link()`	- Update an existing profile filter link. Patch semantics supported
* `ga_filter_view()`	- Get specific filter for view (profile)
* `ga_filter_view_list()`	- List filters for view (profile)


## Goals

* `ga_goal()` -	Get goal
* `ga_goal_list()` -	List goals
* `ga_goal_add()` - Create and add Goals to a web property
* `ga_goal_update()` - Modify an existing goal

## Remarketing segments

* `ga_remarketing_estimate()` -	Estimate number of users added to the segment yesterday
* `ga_remarketing_get()` -	Get a remarketing audience
* `ga_remarketing_list()` -	List remarketing audiences
* `ga_remarketing_build()` - Create definitions to be used within `ga_remarketing_create()`
* `ga_remarketing_create()` - Create a remarketing audience

## Unsampled reports

Available only for GA360 accounts, you will need to authenticate with the Google drive scope to get download access. The download functions are contributed by @j450h1

* `ga_unsampled()` -	Get Unsampled Report Meta Data
* `ga_unsampled_download()` -	Download Unsampled Report from Google Drive
* `ga_unsampled_list()` -	List Unsampled Reports

## Users

* `ga_users_list()` -	List Users for the level you specify
* `ga_clientid_hash()` - Creates the clientID hash that is used in BigQuery GA360 exports
* `ga_user_deletion()` - Delete a website visitor from Google Analytics






