---
title: "Data API for Google Analytics 4 (App+Web)"
---

The Data API and Google Analytics Admin API are used with the Google Analytics 4 properties, the newest version of Google Analytics and evolution from Universal Analytics.  

```{r include=FALSE}
library(googleAnalyticsR)
```


## Features

* Only API to fetch data from Google Analytics 4 properties
* No sampling
* Fewer limits on exports, such as being able to fetch more than 1million rows
* Ability to create your own custom metrics and dimensions
* Send in up to 4 date ranges at once
* Easier integration with the real-time API
* Improved filter syntax

## Meta data

Universal metadata for what you can query via the Data API can be found by specifying that API in the `ga_meta()` function:

```r
metadata <- ga_meta(version = "data")
```

You may have custom dimensions and metrics setup for your web property - to get a list of those specify the web property in the meta data call:

```r
# Google Analytics 4 metadata for a particular Web Property
ga_meta("data", propertyId = 206670707)
```

## Fetching data

Make sure to authenticate first using `ga_auth()` or otherwise.

The primary data fetching function is `ga_data()`

You need your propertyId to query data, and then at least a metric and date range:

```r
# replace with your propertyId
my_property_id <- 206670707
basic <- ga_data(
  my_property_id,
  metrics = c("activeUsers","sessions"),
  date_range = c("2020-03-31", "2020-04-27")
  )
```

Dimensions can be added to split out your results:

```r
# split out metrics by the dimensions specified
dimensions <- ga_data(
    my_property_id,
    metrics = c("activeUsers","sessions"),
    dimensions = c("date","city","dayOfWeek"),
    date_range = c("2020-03-31", "2020-04-27")
)
```

By default the API returns 100 results.  Add the `limit` parameter to change the number of results returned.  To get all results, use -1

```r
only_10 <- ga_data(
    my_property_id,
    metrics = c("activeUsers","sessions"),
    dimensions = c("date","city","dayOfWeek"),
    date_range = c("2020-03-31", "2020-04-27"),
    limit = 10
)

all_results <- ga_data(
    my_property_id,
    metrics = c("activeUsers","sessions"),
    dimensions = c("date","city","dayOfWeek"),
    date_range = c("2020-03-31", "2020-04-27"),
    limit = -1
)
```

## Filters

Filters are simpler to create but more flexible that in Universal Analytics. 

There are now only two filter functions - `ga_aw_filter()` and `ga_aw_filter_expr()`.  As was the case for `google_analytics()` , you use the filter functions to construct metric filters or dimension filters in the `dimensionFilter` or `metricFilter` parameters. Do not construct metric filters and use in the `dimensionFilter` argument or vice-versa.

### Making filter elements

The base object is `ga_aw_filter()` - this holds the logic for the specific metric or dimension you are using.  The function will check your filter object based on the R class of the object you are passing in as its value:

* `character`: stringFilter - e.g. `"Copenhagen"`
* `character vector`: inListFilter e.g. `c("Copenhagen","London","New York")`
* `numeric`: NumericFilter e.g. `5`
* `numeric 2-length vector`: BetweenFilter e.g. `c(5, 10)`
* `logical`: TRUE will filter for NULL e.g. `TRUE`

e.g. if you pass in a character of length one (`"Copenhagen"`) then it will assume to be a class `StringFilter` (all dimensions that match "Copenhagen") if you pass in a character of length greater than one `c("Copenhagen","London","New York")`, then it assume to be a class `InListFilter` (dimensions must match one in the list)

Ensure the comparison operation you are using makes sense for the type of value:

* string filters: `"EXACT","BEGINS_WITH","ENDS_WITH","CONTAINS","FULL_REGEXP", "PARTIAL_REGEXP"`
* numeric filters: `"EQUAL", "LESS_THAN", "LESS_THAN_OR_EQUAL", "GREATER_THAN", "GREATER_THAN_OR_EQUAL"`

### Using filter elements

All filters are made up of filter expressions using `ga_aw_filter_expr()`, but if you want just one filter, use `ga_aw_filter()` directly in your GA call.

```r
simple_filter <- ga_data(
   206670707,
   metrics = c("activeUsers","sessions"),
   dimensions = c("date","city","dayOfWeek"),
   date_range = c("2020-03-31", "2020-04-27"),
   dimensionFilter = ga_aw_filter("city", "Copenhagen", "EXACT"),
   limit = 100
   )
```

If you need more complicated filters, then build them using `ga_aw_filter_expr()`.  This lets you combine `ga_aw_filter()` objects in various ways.


```{r}
ga_aw_filter_expr(
  ga_aw_filter("city", "Copenhagen", "EXACT")
  )

ga_aw_filter_expr(
  ga_aw_filter("dayOfWeek", "4", "EXACT"),
  ga_aw_filter("dayOfWeek", "5", "EXACT"),
  type = "or") 
   
# equivalent to above as uses InList filter
multiple_or2 <- ga_aw_filter_expr(
  ga_aw_filter("dayOfWeek", c("4","5"))
  )
multiple_or2

# make a filter expression then pass it again with type='not' to negate it 
ga_aw_filter_expr(multiple_or2, type = "not")

# or directly - 
clean_city <- ga_aw_filter_expr(
  ga_aw_filter("city", "(not set)", "EXACT",), 
  type = "not")
clean_city
```

You can also recursively nest filter expressions - this lets you build up complex filters:

```{r}
# use previously created filters to build another filter expression:
ga_aw_filter_expr(multiple_or2, clean_city)
```


## Real Time Data

Real-time data can be fetched with the same function as the regular Data API, but it is calling another endpoint.  Add the `realtime=TRUE` argument to the function.

A limited subset of [dimensions and metrics are available in the real-time API](https://developers.google.com/analytics/devguides/reporting/data/v1/realtime-api-schema).  Date ranges are ignored.

```r
# run a real-time report 
realtime <- ga_data(
  206670707,
  metrics = "activeUsers",
  dimensions = "city",
  dimensionFilter = ga_aw_filter("city", "Copenhagen", "EXACT"),
  limit = 100,
  realtime = TRUE)
```