---
title: "Data API for Google Analytics 4 (App+Web)"
---

The [Data API](https://developers.google.com/analytics/devguides/reporting/data/v1) and [Google Analytics Admin API](https://developers.google.com/analytics/devguides/config/admin/v1) are used with the Google Analytics 4 properties, the newest version of Google Analytics and evolution from Universal Analytics.  

```{r include=FALSE}
library(googleAnalyticsR)
```


## Google Analytics 4 - Data API Features

* Only API to fetch data from Google Analytics 4 properties
* No sampling
* Fewer limits on exports, such as being able to fetch more than 1million rows
* Ability to create your own custom metrics and dimensions
* Send in up to 4 date ranges at once
* Easier integration with the real-time API
* Improved filter syntax

## Meta data for GA4

Universal metadata for what you can query via the Data API can be found by specifying that API in the `ga_meta()` function:

```r
metadata <- ga_meta(version = "data")
```

You may have custom dimensions and metrics set up for your web property - to get a list of those specify the web property in the meta data call:

```r
# Google Analytics 4 metadata for a particular Web Property
ga_meta("data", propertyId = 206670707)
```

Custom events and user scoped custom dimensions have names starting with `customEvent:` and `customUser:` respectively.  Include them in your reports with the prefix.

## Fetching GA4 Data into R

Make sure to authenticate first using `ga_auth()` or otherwise.

The primary data fetching function is `ga_data()`

You need your `propertyId` to query data, and then at least a metric and date range:

```r
# replace with your propertyId
my_property_id <- 206670707
basic <- ga_data(
  my_property_id,
  metrics = c("activeUsers","sessions"),
  date_range = c("2020-03-31", "2020-04-27")
  )
  
basic
# A tibble: 1 x 2
#  activeUsers sessions
#        <dbl>    <dbl>
#1        1716     2783
```

Dimensions can be added to split out your results:

```r
# split out metrics by the dimensions specified
dimensions <- ga_data(
    my_property_id,
    metrics = c("activeUsers","sessions"),
    dimensions = c("date","city","dayOfWeek"),
    date_range = c("2020-03-31", "2020-04-27")
)

dimensions
# A tibble: 100 x 5
#   date       city      dayOfWeek activeUsers sessions
#   <date>     <chr>     <chr>           <dbl>    <dbl>
# 1 2020-04-08 (not set) 4                  18       21
# 2 2020-04-08 Rome      4                  12       14
# 3 2020-04-15 (not set) 4                   9       11
# 4 2020-04-27 (not set) 2                   9       11
# 5 2020-04-09 (not set) 5                   8       10
# 6 2020-04-14 (not set) 3                   8        8
# 7 2020-04-22 (not set) 4                   8        9
# 8 2020-03-31 (not set) 3                   7       10
# 9 2020-04-08 Bologna   4                   7        7
#10 2020-04-07 (not set) 3                   6        7
# … with 90 more rows
```

### Row limits

By default the API returns 100 results.  Add the `limit` parameter to change the number of results returned.  To get all results, use -1

```r
only_5 <- ga_data(
    my_property_id,
    metrics = c("activeUsers","sessions"),
    dimensions = c("date","city","dayOfWeek"),
    date_range = c("2020-03-31", "2020-04-27"),
    limit = 5
)

only_5
# A tibble: 5 x 5
#  date       city      dayOfWeek activeUsers sessions
#  <date>     <chr>     <chr>           <dbl>    <dbl>
#1 2020-04-08 (not set) 4                  18       21
#2 2020-04-08 Rome      4                  12       14
#3 2020-04-15 (not set) 4                   9       11
#4 2020-04-27 (not set) 2                   9       11
#5 2020-04-09 (not set) 5                   8       10

all_results <- ga_data(
    my_property_id,
    metrics = c("activeUsers","sessions"),
    dimensions = c("date","city","dayOfWeek"),
    date_range = c("2020-03-31", "2020-04-27"),
    limit = -1
)

all_results
# A tibble: 1,763 x 5
#   date       city      dayOfWeek activeUsers sessions
#   <date>     <chr>     <chr>           <dbl>    <dbl>
# 1 2020-04-08 (not set) 4                  18       21
# 2 2020-04-08 Rome      4                  12       14
# 3 2020-04-15 (not set) 4                   9       11
# 4 2020-04-27 (not set) 2                   9       11
# 5 2020-04-09 (not set) 5                   8       10
# 6 2020-04-14 (not set) 3                   8        8
# 7 2020-04-22 (not set) 4                   8        9
# 8 2020-03-31 (not set) 3                   7       10
# 9 2020-04-08 Bologna   4                   7        7
#10 2020-04-07 (not set) 3                   6        7
# … with 1,753 more rows
```

### Custom definitions

When fetching custom dimensions and metrics, specify the prefix as you read it in the meta data table.  See this [Google article on custom definitions](https://developers.google.com/analytics/devguides/reporting/data/v1/advanced#listing_custom_definitions_and_creating_reports) for details.

```r
# will include your custom data
my_meta <- ga_meta("data", propertyId = 206670707)

custom <- ga_data(
    my_property_id,
    metrics = c("customEvent:credits_spent"),
    dimensions = c("date","customUser:last_level","customEvent:achievement_id"),
    date_range = c("2020-03-31", "2020-04-27"),
    limit = -1
)
```

## Date Ranges

You can send in up to 4 date ranges, via a vector of dates:

```r
date_range4 <- ga_data(
    my_property_id,
    metrics = c("activeUsers","sessions"),
    dimensions = c("date","city","dayOfWeek"),
    date_range = c("2020-03-31", "2020-04-06", 
                   "2020-04-07", "2020-04-14", 
                   "2020-04-15", "2020-04-22", 
                   "2020-04-23", "2020-04-30"),
    limit = -1
)
```

The date is output with a `dateRange` column indicating which date ranges the data belongs to:

```r
date_range4
# A tibble: 7,948 x 6
#   date       city            dayOfWeek dateRange    activeUsers sessions
#   <date>     <chr>           <chr>     <chr>              <dbl>    <dbl>
# 1 2020-04-06 Laval           2         date_range_0           1        1
# 2 2020-04-29 Ghent           4         date_range_3           1        1
# 3 2020-03-31 Wokingham       3         date_range_0           1        1
# 4 2020-04-01 Zielona Gora    4         date_range_0           1        1
# 5 2020-04-16 Charlottesville 5         date_range_2           1        1
# 6 2020-04-25 Fulshear        7         date_range_3           1        1
# … with 7,938 more rows
```

You can send in dates as strings in YYYY-MM-DD format; as R Dates (e.g. `Sys.Date()` or via the API keywords "today", "yesterday", or "NdaysAgo")


```r
# use R to make useful date vectors
dates <- rev(seq(Sys.Date(), by = -7, length.out = 8))
dates
#[1] "2020-10-19" "2020-10-26" "2020-11-02" "2020-11-09" "2020-11-16" "2020-11-23" "2020-11-30" "2020-12-07"

# r dates
ga_data(
    my_property_id,
    metrics = c("activeUsers","sessions"),
    dimensions = c("date","city","dayOfWeek"),
    date_range = dates,
    limit = -1
)


# text dates
ga_data(
    my_property_id,
    metrics = c("activeUsers","sessions"),
    dimensions = c("date","city","dayOfWeek"),
    date_range = c("yesterday","today","3daysAgo","2daysAgo"),
    limit = -1)
```


## Filters

Filters are simpler to create but more flexible than in Universal Analytics. 

There is now only one filter function - `ga_data_filter()`.  As was the case for `google_analytics()` , you use the filter function to construct metric filters or dimension filters in the `dimensionFilter` or `metricFilter` parameters in your `ga_data()` call. 

### Making filter elements

The base object is `ga_data_filter()` - this holds the logic for the specific metric or dimension you are using.  The function uses a new DSL for GA4 filters, the syntax rules are detailed below: 

* A single filter, or multiple filters within a filter expression can be passed in to `ga_data()`
* The single filter syntax is (field) (operator) (value) e.g. `city=="Copenhagen"`
* (field) is a dimension or metric for your web property, which you can review via `ga_meta("data")`
* (field) can be quoted (`"city"`, `"session"`), or unquoted ( `city` or `session`) if you want to use validation.
* (field) validation for unquoted fields is available if using default metadata (e.g. `city` or `session`), or you have fetched your custom fields via `ga_meta("data", propertyId=123456)`
* (operator) can be one of `==, >, >=, <, <=` for metrics
* (operator) can be one of `==, %begins%, %ends%, %contains%, %contains%, %regex%, %regex_partial%` for dimensions
* dimension (operator) are by default case sensitive. Make them case insensitive by using UPPER case variations `%BEGINS%, %ENDS%` etc. or `%==%` for case insensitive exact matches
* (value) can be strings (`"dim1"`), numerics (`55`), string vectors (`c("dim1", "dim2")`), numeric vectors (`c(1,2,3)`) or boolean (`TRUE`) which will correspond to different types of filters
* Filter expressions for multiple filters when using the operators: `&, |, !` which correspond to `AND`, `OR` and `NOT` respectively. 

#### Filter Fields

Fields are metrics and dimensions that are available to your GA4 implementation, including custom fields.  You can see what is available by calling the `ga_meta("data")` function.

Do not construct metric filters and use in the `dimensionFilter` argument or vice-versa.

You can use quoted (`"city"`, `"session"`) or unquoted fields ( `city` or `session`) which will check the field is valid before you send it to the API.  

If you want to use custom fields from your property, do a call to `ga_meta("data", propertyId=1234546)` replacing your propertyId for the GA4 property that has the custom fields.  Once fetched, they will be placed in your local environment for all future calls to `ga_data_filter()` - use the custom events without the `customEvent:` prefix e.g.

```r
# gets fields including custom event field "customEvent:test_dim"
my_meta <- ga_meta("data", propertyId = 206670707)

# use the custom event in a filter
ga_data_filter(test_dim == "test")
```

#### Filter Values

Values are checked in the filter object based on the R class of the object you are passing in as its value:

* `character`: stringFilter - e.g. `"Copenhagen"`
* `character vector`: inListFilter e.g. `c("Copenhagen","London","New York")`
* `numeric`: NumericFilter e.g. `5`
* `numeric 2-length vector`: BetweenFilter e.g. `c(5, 10)`
* `logical`: TRUE will filter for NULL e.g. `TRUE`

e.g. if you pass in a character of length one (`"Copenhagen"`) then it will assume to be a class `StringFilter` (all dimensions that match "Copenhagen") if you pass in a character of length greater than one `c("Copenhagen","London","New York")`, then it assume to be a class `InListFilter` (dimensions must match one in the list)

### Examples Using GA4 Filters

All filters are made up of filter expressions using `ga_data_filter()`:

```r
simple_filter <- ga_data(
   206670707,
   metrics = c("activeUsers","sessions"),
   dimensions = c("date","city","dayOfWeek"),
   date_range = c("2020-03-31", "2020-04-27"),
   dimensionFilter = ga_data_filter(city=="Copenhagen"),
   limit = 100
   )

simple_filter
# A tibble: 17 x 5
#   date       city       dayOfWeek activeUsers sessions
#   <date>     <chr>      <chr>           <dbl>    <dbl>
# 1 2020-04-16 Copenhagen 5                   3        4
# 2 2020-04-10 Copenhagen 6                   2        2
# 3 2020-04-15 Copenhagen 4                   2        2
# 4 2020-04-17 Copenhagen 6                   2        2
# ...
```

If you need more complicated filters, then build them using the DSL syntax.  This lets you combine `ga_data_filter()` objects in various ways.


```{r}
## filter clauses
# OR string filter
ga_data_filter(city=="Copenhagen" | city == "London")
# inlist string filter
ga_data_filter(city==c("Copenhagen","London"))
# AND string filters
ga_data_filter(city=="Copenhagen" & dayOfWeek == "5")
# NOT string filter
ga_data_filter(!(city=="Copenhagen" | city == "London"))

# multiple filter clauses
ga_data_filter(city==c("Copenhagen","London","Paris","New York") &
                 (dayOfWeek=="5" | dayOfWeek=="6"))
```

#### Filter field validation

Validation is carried out if the field is unquoted.  If you don't want validation use quotes.  

```{r}
# validation of fields - correct
ga_data_filter(city=="Copenhagen")

# validation of fields - error
tryCatch(ga_data_filter(cittty=="Copenhagen"), 
         error = function(err) err$message)

# avoid validation by quoting
ga_data_filter("cittty"=="Copenhagen")
```

For custom fields use `ga_meta("data", propertyId=12345)` first to fetch them.

```r
# gets fields including custom event field "customEvent:test_dim"
my_meta <- ga_meta("data", propertyId = 206670707)

# use the custom event in a filter
ga_data_filter(test_dim == "test")
```

#### Numeric filters for use in `metricFilters`

An example of metric filters are below:

```r
metric_filter <- ga_data(
   206670707,
   metrics = c("activeUsers","sessions"),
   dimensions = c("date","city","dayOfWeek"),
   date_range = c("2020-03-31", "2020-04-27"),
   metricFilter = ga_data_filter(sessions>10),
   limit = 100
   )

metric_filter
# A tibble: 7 x 5
#  date       city      dayOfWeek activeUsers sessions
#  <date>     <chr>     <chr>           <dbl>    <dbl>
#1 2020-04-08 (not set) 4                  18       21
#2 2020-04-08 Rome      4                  12       14
#3 2020-04-15 (not set) 4                   9       11
#4 2020-04-27 (not set) 2                   9       11
# ...
```

```{r}
## numeric filter types
# numeric equal filter
ga_data_filter(sessions==5)
# between numeric filter
ga_data_filter(sessions==c(5,6))
# greater than numeric
ga_data_filter(sessions > 0)
# greater than or equal
ga_data_filter(sessions >= 1)
# less than numeric
ga_data_filter(sessions < 100)
# less than or equal numeric
ga_data_filter(sessions <= 100)
```

#### Dimension filters for use in `dimensionFilters`

All the string filters that can be used are below:

```{r}
## string filter types
# begins with string
ga_data_filter(city %begins% "Cope")
# ends with string
ga_data_filter(city %ends% "hagen")
# contains string
ga_data_filter(city %contains% "ope")
# regex (full) string
ga_data_filter(city %regex% "^Cope")
# regex (partial) string
ga_data_filter(city %regex_partial% "ope")
```

By default string filters are case sensitive.  Use UPPERCASE operator to make then case insensitive

```{r}
# begins with string (case insensitive)
ga_data_filter(city %BEGINS% "cope")
# ends with string (case insensitive)
ga_data_filter(city %ENDS% "Hagen")
# case insensitive exact match
ga_data_filter(city %==% "copeNHAGen")
```

#### Complex filters

You can also recursively nest filter expressions to make more complicated ones.  

The filter below looks for visitors from Copenhagen, London, Paris or New York who arrived on day 5 or 6 of the week, from Google referrers but not including Google Ads.

```{r}
# use previously created filters to build another filter expression:
# multiple filter clauses
f1 <- ga_data_filter(city==c("Copenhagen","London","Paris","New York") &
                       (dayOfWeek=="5" | dayOfWeek=="6")) 

# build up complicated filters
f2 <- ga_data_filter(f1 | sessionSource=="google")
f3 <- ga_data_filter(f2 & !sessionMedium=="cpc")
f3
```

You can use filter expression objects above directly like so:

```r
complex_filter <- ga_data(
   206670707,
   metrics = c("activeUsers","sessions"),
   dimensions = c("date","city","dayOfWeek"),
   date_range = c("2020-03-31", "2020-04-27"),
   dimensionFilter = f3,
   limit = 100
   )
   
complex_filter
# A tibble: 100 x 5
#   date       city      dayOfWeek activeUsers sessions
#   <date>     <chr>     <chr>           <dbl>    <dbl>
# 1 2020-04-09 London    5                   6        7
# 2 2020-04-14 (not set) 3                   6        6
# 3 2020-04-22 (not set) 4                   6        7
# 4 2020-04-15 (not set) 4                   5        6
# ...
```

## Real Time Data

Real-time data can be fetched with the same function as the regular Data API, but it is calling another endpoint.  Add the `realtime=TRUE` argument to the function.

A limited subset of [dimensions and metrics are available in the real-time API](https://developers.google.com/analytics/devguides/reporting/data/v1/realtime-api-schema).  Date ranges are ignored.

```r
# run a real-time report 
realtime <- ga_data(
  206670707,
  metrics = "activeUsers",
  dimensions = "city",
  dimensionFilter = ga_data_filter(city=="Copenhagen"),
  limit = 100,
  realtime = TRUE)
```

## Metric Aggregations

Each API call includes the TOTAL, MAXIMUM and MINIMUM metric aggregations in the returned data.frame's metadata.  You can access this data using base R's `attr()` function or use `ga_data_aggregations()` to extract the data.frames:

```r
aggs <- ga_data(
      206670707, 
      date_range = c(Sys.Date() - 4, Sys.Date() - 1),
      metrics = "activeUsers",
      dimensions = c("city","unifiedScreenName"),
      limit = 100)
      
all_aggs <- ga_data_aggregations(aggs, type = "all")
all_aggs
#$totals
## A tibble: 1 x 4
#  city           unifiedScreenName dateRange    activeUsers
#  <chr>          <chr>             <chr>              <dbl>
#1 RESERVED_TOTAL RESERVED_TOTAL    date_range_0         250
#
#$maximums
## A tibble: 1 x 4
#  city         unifiedScreenName dateRange    activeUsers
#  <chr>        <chr>             <chr>              <dbl>
#1 RESERVED_MAX RESERVED_MAX      date_range_0           4
#
#$minimums
## A tibble: 1 x 4
#  city         unifiedScreenName dateRange    activeUsers
#  <chr>        <chr>             <chr>              <dbl>
#1 RESERVED_MIN RESERVED_MIN      date_range_0           0

# now in a list
all_aggs$totals
## A tibble: 1 x 4
#  city           unifiedScreenName dateRange    activeUsers
#  <chr>          <chr>             <chr>              <dbl>
#1 RESERVED_TOTAL RESERVED_TOTAL    date_range_0         250

# extract individual aggregations individually
maxes <- ga_data_aggregations(aggs, type = "maximums")
maxes
## A tibble: 1 x 4
#  city         unifiedScreenName dateRange    activeUsers
#  <chr>        <chr>             <chr>              <dbl>
#1 RESERVED_MAX RESERVED_MAX      date_range_0           4
```

If you request more than one date range, the aggregations will be calculated for each one:

```r
# use R to generate some dates
dates <- rev(seq(Sys.Date(), by = -7, length.out = 8))
dates
#[1] "2020-10-19" "2020-10-26" "2020-11-02" "2020-11-09" "2020-11-16" "2020-11-23" "2020-11-30" "2020-12-07"

aggs <- ga_data(
    206670707, date_range = dates,
    metrics = "activeUsers",
    dimensions = c("city","unifiedScreenName"),
    limit = 100)
    
# get the totals
ga_data_aggregations(aggs, type = "totals")
## A tibble: 4 x 4
#  city           unifiedScreenName dateRange    activeUsers
#  <chr>          <chr>             <chr>              <dbl>
#1 RESERVED_TOTAL RESERVED_TOTAL    date_range_0         200
#2 RESERVED_TOTAL RESERVED_TOTAL    date_range_1           4
#3 RESERVED_TOTAL RESERVED_TOTAL    date_range_2           2
#4 RESERVED_TOTAL RESERVED_TOTAL    date_range_3         399
```

## Quotas

There is no sampling but there are token quotas for API fetches on a per-project basis.  Normally these are not visible until you are close to the quota limits, but you can see them if you set the googleAuthR verbose level below 3 (`options(googleAuthR.verbose=2)`))

The bigger and more complex the query you make, the more tokens you use.

An example taken from above:

```r
options(googleAuthR.verbose=2)
complex_filter <- ga_data(
     206670707,
     metrics = c("activeUsers","sessions"),
     dimensions = c("date","city","dayOfWeek"),
    date_range = c("2020-03-31", "2020-04-06", 
                   "2020-04-07", "2020-04-14", 
                   "2020-04-15", "2020-04-22", 
                   "2020-04-23", "2020-04-30"),
     dimensionFilter = f3,
     limit = 100
)
#>ℹ 2020-11-24 16:12:36 > tokensPerDay: Query Cost [ 15 ] / Remaining [ 24847 ]
#>ℹ 2020-11-24 16:12:36 > tokensPerHour: Query Cost [ 15 ] / Remaining [ 4967 ]
#>ℹ 2020-11-24 16:12:36 > concurrentRequests:  10  / 10
#>ℹ 2020-11-24 16:12:36 > serverErrorsPerProjectPerHour:  10  / 10
```

The quotas are:

* `tokensPerDay` - how many tokens in 24hrs
* `tokensPerHour` - how many tokens in 1 hr
* `concurrentRequests` - how many API requests at once
* `serverErrorsPerProjectPerHour` - how many bad API calls you can make per project/hr

